### 2022-06-27 tex/notes.tex
just pushing everything

\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\section{Softmax Transform}
\textit{Roughly writing the algebra for the idea that Bob Proposed}

>>>>

\usepackage{aistats2021}
\usepackage{amsmath}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\section{Introduction}

\section{Constraints}
\subsection{Bounded Constraints}
\subsection{Simplex Constraints}
\subsection{Definite Matrix constraints}
\section{Softmax Transform}

The softmax function can be understood from Multinomial Logistic Regression employed for predicting probabilities of a Categorically distributed variable. Geometrically it maps $R^K$ to the boundary of a unit K-simplex(it is simply the convex hull of $k+1$ affinely independent points in $R^K$. Essentially it transforms a vector of size K to another vector of size K where the outputs sum to 1. It is worth noting that the mapping is actually from $R^K$ to $R^{K-1}$, so when a vector of size $K$ is transformed the $K_th$ vector is simply $1$- sumofk-1 vectors
R
